---
  output:
    md_document:
      variant: markdown_github
---
  
  ```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figure/",
  fig.height = 1
)
```
# Holiday snap palettes

Here are some pallettes I have made from my own holiday snaps. This is based on the excellent wespalette package and is for personal use only.

## Installation


## Usage

```{r, palettes_dummy}
library("snapalette")
# See all palettes
names(snapalettes)
```

## Palettes

### Mosaic from Fiocruz

```{r, mosaic}
snapalette("Mosaic")
```

### EspiritoSanta

```{r, espirito}
snapalette("EspiritoSanta")
```

### Street art

```{r, royal}
snapalette("ST_art")
```


### Discovery Suites

```{r, discovery}
snapalette("DiscoverySuites")
```


### Ipanama sunset

```{r, sunset}
snapalette("IpanemaSunset")
```

### Orchid

```{r, orchid}
snapalette("Orchid")
```

### Greek cave house

```{r, Cave}
snapalette("CaveHouse")
```

### Kalypso

```{r, Kalypso}
snapalette("Kalypso")
```

```{r, volcano, fig.height = 5}
pal <- snapalette("Kalypso", 21, type = "continuous")
image(volcano, col = rev(pal))
```

### ThiraJazz

```{r, jazz}
snapalette("ThiraJazz")
```

### Camden

```{r, Camden}
snapalette("Camden")
```

### Venice

```{r, venice}
snapalette("Venice")
```

### Barcelona

```{r, Barcelona}
snapalette("Barcelona")
```

```{r ggplot, fig.height=5}
library("ggplot2")
ggplot(mtcars, aes(factor(cyl), fill=factor(gear))) +  geom_bar() +
scale_fill_manual(values =snapalette("Barcelona"))

```

### Fjord

```{r, fjord}
snapalette("Fjord")
```

### Stavanger

```{r, stavanger}
snapalette("Stavanger")
```

### Sweet Shop

```{r, sweetshop}
snapalette("SweetShop")
```

### Wales

```{r, wales}
snapalette("Wales")
```

### Szimpla Kert

```{r, szimpla}
snapalette("SzimplaKert")
```

### Budapest Citadel

```{r, citadel}
snapalette("BudapestCitadel")
```

### Ipanama

```{r, ipanema}
snapalette("Ipanema")
```